Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-12 paper/paper.Rmd
fix figure caption
re-explain why obs need to be omitted in LLTO

```{r tile, fig.cap="Spatial tiling with arguments `rows` and `cols`.", out.width="40%", fig.pos="ht"}
resampling_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))

@@

The "Leave-Location-and-Time-Out" (LLTO) method combines both "Leave-Time-Out" (LTO) and "Leave-Location-Out" (LLO).
It creates partitions that operate on spatiotemporal clusters to reduce both spatial and temporal autocorrelation.
To achieve this, observations are omitted and only a subset is used.
In the special scenario with five temporal levels and five folds, the train/test split happens only at one temporal level (Fig. \@ref(fig:llto)).

@@

- `coordinate_names`: Names of the features which represent the spatial coordinates.
  This is automatically inferred when a `sf` object is passed.
- `coords_as_features`: Whether the coordinates should be used as features during modeling.
  By default coordinates are not used as predictors.
- `crs`: The coordinate reference system of the data. Valid inputs are PROJ4 strings or EPSG codes in the format `ESPG:<code>`.

>>>>

```{r tile, fig.cap="Spatial tiling", out.width="40%", fig.pos="ht"}
resampling_tiles = rsmp("spcv_tiles", nsplit = c(3L, 4L))

@@

The "Leave-Location-and-Time-Out" (LLTO) method combines both "Leave-Time-Out" (LTO) and "Leave-Location-Out" (LLO).
It creates partitions that operate on spatiotemporal clusters to reduce both spatial and temporal autocorrelation.
To achieve this, observations need to be omitted as the split in test and train sets only provides one dimension to separate observations whereas two (space and time) are needed.
In other words, accounting for one dimension as in Fig. \@ref(fig:lto) or Fig. \@ref(fig:llo), by only having one time step or location in either test or training set, would have no effect on the respective other.
To achieve an effect for both, observations need to be omitted as shown in Fig. \@ref(fig:llto).

@@

- `coordinate_names`: Names of the features which represent the spatial coordinates.
  This is automatically inferred when a `sf` object is passed.
- `coords_as_features`: Whether the coordinates should be used as features during modeling.
  By default coordinates are not used as predictors.
- `crs`: The coordinate reference system of the data. Valid inputs are PROJ strings or EPSG codes in the format `ESPG:<code>`.
